\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy
\title{Group 6 - Milestone 2}
 
\author{Peter Macgregor, s1126155}
 
\maketitle

\section{Your Contribution to the Group}
I spent most of my time developing the vision system, looking ahead to milestone 3.
I worked mainly with Patricia and Kuba, and succeeded in detecting the pitch boundaries,
tracking the ball and all 4 robots by building on code written by Kuba and Patricia detecting the various colors.
I discussed with Aris and Kuba about what information is wanted from the vision system and how to represent the world.

\section{High Points of Your Contribution}
\begin{itemize}
  \item Detecting pitch boundaries.
  \item Tracking ball and robots.
  \item Deciding on world representation.
\end{itemize} 

\section{Areas to Improve}
\begin{itemize}
  \item Need to work efficiently in order to get enough done.
  \item Be aware of how non-vision tasks are progressing and be willing to work on them.
\end{itemize}


\section{Points Awarded to Each Member (out of 5)}
\begin{itemize}
\begin{multicols}{2}
\item Peter Macgregor - 4
\item Patricia Dragan - 3.5
\item Egidijus Skinkys - 4
\item Andrew Leith - 3.5
\item Nursultan Askarbekuly - 3.5
\item Peak Limpiti - 3
\item Zhang Chen - 4
\item Aris Tsialos - 4
\item Kuba Kaszyk - 4.5
\end{multicols}
\end{itemize}

\section{Additional Information}
I also spent the morning of the milestone testing the robot for the final state of the pitch.
My next steps will be to track the direction that the robots are facing,
and integrating the vision system with the rest of the robot's code.

\end{document}

