\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy

\title{Milestone 2 Group 6 Summary}
 
\maketitle
\begin{itemize}
\item Peter Macgregor - 4 - Peter worked mainly on the vision system. He detected the pitch boundaries, and built on code written by Kuba and Patricia to track the locations of the ball and robots. He also helped with final testing before the milestone.
\item Patricia Dragan - 3 - Patricia worked on vision with Peter and Kuba. She succeeded in tracking the blue and yellow colours of the robots. She improved efficiency and created a representation of the world. 
\item Egidijus Skinkys - 4 - Egidijus worked on testing the defender robot as the pitch was constantly changing. He wrote a new class for sending commands to the robot. This will link in with the planning stage, allowing them to abstract the robot commands.
\item Andrew Leith - 3.5 - Andrew worked mainly on getting the bluetooth up and running. Commands can now be sent to the robot, and the system is ready to be integrated with the rest of the project. Andrew also helped with testing for the milestone.
\item Nursultan Askarbekuly - 3.5 - Nursultan built the attacker robot for mileston 2. He built a kicker based on a design from last year and incorporated it into the robot.
\item Peak Limpiti - 3 - Peak built the defender robot for mileston 2, working on making the robot compact while still making the kicker suitable for the milestone.
\item Zhang Chen - 3.5 - Zhang planned with Aris about the high level structure of the project. He researched the pilot class and wrote information for the team. He set up a representation of the pitch in webots for simulation.
\item Aris Tsialos - 3.5 - Aris spent his time planning the AI of the project. He kept in touch with every sub-team and made sure that each part of the project would be able to be integrated together.
\item Kuba Kaszyk - 4.5 - Kuba helped out with vision to begin with and then moved on to thinking about high level design with Aris. They planned representations for each of the objects. He also tested the robot leading up to the milestone.
\end{itemize}


\end{document}

