\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy
\title{Mindstorm Troopers - Milestone 1}
 
\author{Kuba Kaszyk, s1108328}
 
\maketitle

\section{Your Contribution to the Group}
During the past two weeks, I have been working largely on organizational matters for the team, including communications, wiki, email, and timesheet setup. I have set up teams and collaborated with them on design decisions and plan of action. I have also set up the video feed, and started working on recognizing the ball.  

\section{High Points of Your Contribution}
\begin{itemize}
  \item I organized the team structure and split tasks between teams.
  \item I set up the video feed and started working on recognition of the ball.
\end{itemize} 

\section{Areas to Improve}
\begin{itemize}
  \item I would like to delegate tasks better, so I spend less time on organization and more directly working on the project.
  \item I would like to distribute and assign tasks better, so that everyone in the team always has something to work on. 
\end{itemize}


\section{Points Awarded to Each Member (out of 5)}
\begin{itemize}
\begin{multicols}{2}
\item Peter Macgregor - 4
\item Patricia Dragan - 3
\item Egidijus Skinkys - 3
\item Andrew Leith - 3
\item Nursultan Askarbekuly - 4
\item Peak Limpiti - 3
\item Zhang Chen - 3
\item Aris Tsialos - 4
\item Kuba Kaszyk - 5
\end{multicols}
\end{itemize}

\section{Additional Information}
I set early deadlines for all tasks related to milestone 1. All the deadlines I set were kept, and so milestone 1 was completed by Friday. This gave our team additional time to look ahead into the next tasks.



\end{document}

