\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy
\title{Mindstorm Troopers - Milestone 1}
 
\author{Peter Macgregor, s1126155}
 
\maketitle

\section{Your Contribution to the Group}
I spent a lot of my time over the last two week trying to set up vision libraries
in Java and Python. I successfully tracked the ball using a crude python algorithm.
I also contributed to the code used for milestone 1, including slowing the robot down
and adding a second light sensor.

\section{High Points of Your Contribution}
\begin{itemize}
  \item Tracking the ball using the python vision libraries.
  \item Rebuilding the robot and making it drive slower.
  \item Adapting my code to run the boundaries in different directions depending on initial angle.
\end{itemize} 

\section{Areas to Improve}
\begin{itemize}
  \item I need to spend more time working on the vision system.
  \item I need to work more consistently on the project.
\end{itemize}


\section{Points Awarded to Each Member (out of 5)}
\begin{itemize}
\begin{multicols}{2}
\item Peter Macgregor - 4
\item Patricia Dragan - 3
\item Egidijus Skinkys - 3
\item Andrew Leith - 3
\item Nursultan Askarbekuly - 4
\item Peak Limpiti - 3
\item Zhang Chen - 3
\item Aris Tsialos - 4
\item Kuba Kaszyk - 5
\end{multicols}
\end{itemize}

\section{Additional Information}
I also took minutes for our meeting on Friday and intend to continue to do that for every
meeting. I've been put in charge of overseeing vision going forwards, so that should be
my main focus from now on.

\end{document}

