\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy
\title{The Mindstorm Troopers - Milestone 1}
 
\author{Zhang Chen, s1101428}
 
\maketitle

\section{Your Contribution to the Group}
During the last two weeks, I give a first try to this milestone, from both the robot assembling and code aspects. After that, I helped doing experiments with the robots and fixing problems by changing the code or the robot structure.

\section{High Points of Your Contribution}
\begin{itemize}
  \item I wrote basic robot code for the moving and sensors.
  \item I helped building and testing the robot for this milestone.
  \item I did some study about the Lejos API.
  
\end{itemize} 

\section{Areas to Improve}
\begin{itemize}
  \item I would like to focus more on the task I was allocated to do later.
  \item I need to do more study of codes from previous years and learn the best from them.
\end{itemize}


\section{Points Awarded to Each Member (out of 5)}
\begin{itemize}
\begin{multicols}{2}
\item Peter Macgregor - 4
\item Patricia Dragan - 3
\item Egidijus Skinkys - 3
\item Andrew Leith - 3
\item Nursultan Askarbekuly - 4
\item Peak Limpiti - 3
\item Zhang Chen - 3
\item Aris Tsialos - 4
\item Kuba Kaszyk - 5
\end{multicols}
\end{itemize}

\section{Additional Information}
I am working a simulator based on the webots and I believe it will help the AI part later.


\end{document}

