\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy

\title{Milestone 3 Group 6 Summary}
 
\maketitle
\begin{itemize}
\item Peter Macgregor - 3.5 - Peter worked on vision throughout the week. He succesfully tracked the dots to get the orientation of the robots. He also worked on the world class which acts as an interface between vision and AI.
\item Patricia Dragan - 2 - Patricia began woking on vision, she implemented a basic method for finding the dot on the robot. She also worked on implementing the GUI for vision.
\item Egidijus Skinkys - 3.5 - Egidijus wrote tests for the communications. He solved bugs with the bluetooth. He calibrated the robots for acting on the commands which will be sent to them. 
\item Andrew Leith - 3.5 - Andrew finalized the communications and maintained the interface between the computer and the robot. He helped debug when bugs appeared in other people's code to do with communication.
\item Nursultan Askarbekuly - 3 - Nursultan worked with Peak to build the robots. Nur built the attacker for the milestone. He continued to maintain the robot throughout testing.
\item Peak Limpiti - 3 - Peak built the defender from scratch for this milestone. He tested in to make sure it would work with the code from the rest of the team.
\item Zhang Chen - 4 - Roy helped plan the structure of the AI and planning for the robot. He helped build the structure for the AI and implement it with the robots. In particular, he wrote mots of the code for the attacker robot.
\item Aris Tsialos - 4 - Aris headed up the AI team. He had an idea of the high level structure of the system early on. He then created the strategy for the defender. He implemented the geometry package for mathematical processing.
\item Kuba Kaszyk - 3.5 - Kuba facilitated communication between vaious teams. He implemented an interface between the AI and the communications. He helped integrate the whole system and testing before the milestone.
\end{itemize}


\end{document}

