\documentclass[dvips]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{multicol}
\usepackage{layout}
\usepackage[margin=1in]{geometry}

%\setlength{\voffset}{-0.75in}
%\setlength{\headsep}{5pt} 
 
\begin{document}
\sloppy
\title{Group 6 - Milestone 3}
 
\author{Peter Macregor, s1126155}
 
\maketitle

\section{Your Contribution to the Group}
I worked on vision for Milestone 3 throughout this week. The main challenge
was tracking the dot on the robots in order to detect the direction they face.
I tried various methods before settling on the current one which works in most cases.
I also built on the interface between vision and the rest of the system. This
abstracts the information about the world so the AI methods can access it without
reference to the vision system. I also helped with last minute testing on Wednesday morning.

\section{High Points of Your Contribution}
\begin{itemize}
  \item Tracking the dots on the robots with reasonably high accuracy.
  \item Improving the interface to vision.
  \item Reducing the noise on the vision system. Eratic values are handled in a more sophisticated way.
\end{itemize} 

\section{Points Awarded to Each Member (out of 5)}
\begin{itemize}
\begin{multicols}{2}
\item Peter Macgregor - 4
\item Patricia Dragan - 2.5
\item Egidijus Skinkys - 3.5
\item Andrew Leith - 3.5
\item Nursultan Askarbekuly - 3
\item Peak Limpiti - 3
\item Zhang Chen - 3.5
\item Aris Tsialos - 4
\item Kuba Kaszyk - 4
\end{multicols}
\end{itemize}

\section{Additional Information}
My plans for the future: improve the dot tracking algorithm so that it is
more reliable, add GUI for changing camera settings and threshold values,
improve blue robot tracking, add implementation for tracking opponents robots.\\
These tasks should be shared out between Patricia and myself.



\end{document}

